% LaTEX source code
% Last modified November 1st, 2005
% Steve Miller
% note that the percent sign comments out the rest of the line
% first, we set a document class. often use 12pt characters, though
% sometimes people do 11 or 10. you can do report or article, both similar
%\documentclass[12pt,letterpaper]{article}
\documentclass[12pt,reqno]{amsart}
\linespread{1}
\addtolength{\textwidth}{2cm} \addtolength{\hoffset}{-1cm}
\addtolength{\marginparwidth}{-1cm} \addtolength{\textheight}{2cm}
\addtolength{\voffset}{-1cm}
% below are some packages that are needed for certain symbols, graphics, colors.
% safest to just include these.
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{mathrsfs}
\usepackage{latexsym}
\usepackage[dvips]{graphics}
\usepackage{epsfig}
\usepackage{hyperref, amsmath, amsthm, amsfonts, amscd, flafter,epsf}
\usepackage{amsmath,amsfonts,amsthm,amssymb,amscd}
\input amssym.def
\input amssym.tex
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{url}
\usepackage{floatrow}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{capt-of}
\usepackage{physics}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{(#1)}}}

    %=======================================================

    %   THIS IS WHERE YOU PUT SHORTCUT DEFINITIONS

    %========================================================

% Note that we use a percent sign to comment out a line

% below are shortcut commands

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% below are shortcuts for equation, eqnarray,

% itemize and enumerate environments

\newcommand\be{\begin{equation}}
\newcommand\ee{\end{equation}}
\newcommand\bea{\begin{eqnarray}}
\newcommand\eea{\end{eqnarray}}
\newcommand\bi{\begin{itemize}}
\newcommand\ei{\end{itemize}}
\newcommand\ben{\begin{enumerate}}
\newcommand\een{\end{enumerate}}
\newcommand{\ncr}[2]{\left({#1 \atop #2}\right)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Theorem / Lemmas et cetera

\newtheorem{thm}{Theorem}[section]
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{exa}[thm]{Example}
\newtheorem{defi}[thm]{Definition}
\newtheorem{exe}[thm]{Exercise}
\newtheorem{rek}[thm]{Remark}
\newtheorem{que}[thm]{Question}
\newtheorem{prob}[thm]{Problem}
\newtheorem{cla}[thm]{Claim}
\newtheorem{defis}[thm]{Definitions}
\newtheorem{res}[thm]{Result}
\newtheorem{calc}[thm]{Calculation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% shortcuts to environments

% this allows you to do textboldface: simply type \tbf{what you want in bold}

\newcommand{\tbf}[1]{\textbf{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% shortcut to twocase and threecase definitions

\newcommand{\twocase}[5]{#1 \begin{cases} #2 & \text{#3}\\ #4
&\text{#5} \end{cases}   }
\newcommand{\threecase}[7]{#1 \begin{cases} #2 &
\text{#3}\\ #4 &\text{#5}\\ #6 &\text{#7} \end{cases}   }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Blackboard Letters

\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\Z}{\ensuremath{\mathbb{Z}}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\W}{\mathbb{W}}
\newcommand{\Qoft}{\mathbb{Q}(t)}  %use in linux
\newcommand{\soln}{\noindent \textbf{Solution:}\ }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Finite Fields and Groups

\newcommand{\Fp}{ \F_p }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Fractions

\newcommand{\foh}{\frac{1}{2}}  %onehalf
\newcommand{\fot}{\frac{1}{3}}
\newcommand{\fof}{\frac{1}{4}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Legendre Symbols

\newcommand{\js}[1]{ { \underline{#1} \choose p} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% matrix shortcuts

\newcommand{\mattwo}[4]
{\left(\begin{array}{cc}
                        #1  & #2   \\
                        #3 &  #4
                          \end{array}\right) }
\newcommand{\matthree}[9]
{\left(\begin{array}{ccc}
                        #1  & #2 & #3  \\
                        #4 &  #5 & #6 \\
                        #7 &  #8 & #9
                          \end{array}\right) }
\newcommand{\dettwo}[4]
{\left|\begin{array}{cc}
                        #1  & #2   \\
                        #3 &  #4
                          \end{array}\right| }
\newcommand{\detthree}[9]
{\left|\begin{array}{ccc}
                        #1  & #2 & #3  \\
                        #4 &  #5 & #6 \\
                        #7 &  #8 & #9
                          \end{array}\right| }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% greek letter shortcuts

\newcommand{\ga}{\alpha}                  %gives you a greek alpha
\newcommand{\gb}{\beta}
\newcommand{\gep}{\epsilon}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% general functions

\newcommand{\notdiv}{\nmid}               % gives the not divide symbol
\newcommand{\burl}[1]{\textcolor{blue}{\url{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% the following makes the numbering start with 1 in each section;

% if you want the equations numbered 1 to N (without caring about

% what section you are in, comment out the following line.

\numberwithin{equation}{section}

%\textwidth= 6in

%\evensidemargin=37pt

%\oddsidemargin=0pt

\begin{document}



\title{Results Log 9-26-2018 to Present}
\author{Kirk Swanson}
\email{swansonk1@uchicago.edu}
\address{Institute for Molecular Engineering, University of Chicago, 5640 S Ellis Ave, Chicago, IL 60637}
%\keywords{path integral molecular dynamics, path integral monte carlo, metropolis algorithm}
\date{\today}

\maketitle

\section{9/26/2018}
\begin{enumerate}
\item According to Professor de Pablo, the priority item for the path integral research project is to fix the path integral monte carlo barostat in DASH.  So, we will start by investigating the code that Mike has already written for this barostat on the DASH github.
\item First, let's compile the most recent version of DASH on Midway.  Doing "git clone https://github.com/dreid1991/md\_engine.git".  Saving this compiled version on Midway 1 in DASH-9-26-2018.  
\item Information on BoostPython: https://wiki.python.org/moin/boost.python/GettingStarted.  
\subitem The BoostPython library binds C++ and Python in a mostly-seamless fashion.  It is just one member of the boost C++ library collection.  Use the BoostPython library to quickly and easily export C++ to python such that the python interface is very similar to the C++ interface.  Boost.Python bindings are written in pure C++, using no tools other than your editor and your C++ compiler.  
\end{enumerate}

\section{10/1/2018}
\begin{enumerate}
\item Created tip4pF\_9-26-2018.py to run q-TIP4P/F water model in DASH 9/26/2018 version.  
\item Continuing to work on developing this basic test code, checking all possible options to make sure python script is correct.  
\end{enumerate}

\section{10/3/2018}
\begin{enumerate}
\item We will begin by running a series of tests on q-TIP4P/F water.  We will use the following system: 1000 water molecules, 1 ns, initial density of 0.997, temperature of 298 K, pressure 1 atm, printing data every 1000 steps.  We are using run\_9-26-2018.sh and tip4pF\_9-26-2018.py to run DASH version from 9/26/2018.  
\subitem Tests using the Isotropic Monte Carlo Barostat:
\subsubitem Time Step: 0.5, rCut: 9, nBeads: 1, jobname MC-1, restart/traj every 50,000, RUNNING
\subsubitem Time Step: 0.5, rCut: 9, nBeads: 16, jobname MC-2, restart/traj every 50,000, RUNNING
\subsubitem Time Step: 0.5, rCut: 9, nBeads: 32, jobname MC-3, restart/traj every 50,000, RUNNING
\subsubitem Time Step: 0.5, rCut: 12, nBeads: 1, jobname MC-4
\subsubitem Time Step: 0.5, rCut: 12, nBeads: 16, jobname MC-5
\subsubitem Time Step: 0.5, rCut: 12, nBeads: 32, jobname MC-6
\subsubitem Time Step: 0.25, rCut: 9, nBeads: 1, jobname MC-7
\subsubitem Time Step: 0.25, rCut: 9, nBeads: 16, jobname MC-8
\subsubitem Time Step: 0.25, rCut: 9, nBeads: 32, jobname MC-9
\subsubitem Time Step: 1.0, rCut: 9, nBeads: 1, jobname MC-10
\subsubitem Time Step: 1.0, rCut: 9, nBeads: 16, jobname MC-11
\subsubitem Time Step: 1.0, rCut: 9, nBeads: 32, jobname MC-12
\subitem Tests using the Berendsen Barostat:
\subsubitem Time Step: 0.5, rCut: 9, nBeads: 1, jobname B-1
\subsubitem Time Step: 0.5, rCut: 9, nBeads: 16, jobname B-2
\subsubitem Time Step: 0.5, rCut: 9, nBeads: 32, jobname B-3
\subsubitem Time Step: 0.5, rCut: 12, nBeads: 1, jobname B-4
\subsubitem Time Step: 0.5, rCut: 12, nBeads: 16, jobname B-5
\subsubitem Time Step: 0.5, rCut: 12, nBeads: 32, jobname B-6
\subsubitem Time Step: 0.25, rCut: 9, nBeads: 1, jobname B-7
\subsubitem Time Step: 0.25, rCut: 9, nBeads: 16, jobname B-8
\subsubitem Time Step: 0.25, rCut: 9, nBeads: 32, jobname B-9
\subsubitem Time Step: 1.0, rCut: 9, nBeads: 1, jobname B-10
\subsubitem Time Step: 1.0, rCut: 9, nBeads: 16, jobname B-11
\subsubitem Time Step: 1.0, rCut: 9, nBeads: 32, jobname B-12
\item On /home/swansonk1, Midway 1, go into openmm folder.  On depablo-gpu, module load Anaconda3, source activate openmm-env.  Downloaded pimd.py from Markland, called it pimd\_original.py, and created new file pimd\_modified.py.  In the modified file, we change the nonbondedCutoff to 0.9*nanometers, comment out the platform and properties assignments (so that we use OpenCL by default), and change the Simulation() to get rid of platform and properties arguments.  
\item Searching for OpenMM code here: http://docs.openmm.org/development/api-python/
\item Found RPMDMonteCarloBarostat.  "This class is very similar to MonteCarloBarostat, but it is specifically designed for use with RPMDIntegrator.  For each trial move, it scales all copies of the system by the same amount, then accepts or rejects the move based on the change to the total energy of the ring polymer."
\item Having trouble understanding the kinetic energy units in DASH...not sure what is going on here.  I just want to compute the total kinetic energy.  For now we will leave it out then.  
\end{enumerate}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}